DataGatheringandAnalysis

### 2014-11-11 GEMDataSource.Rmd
Changed percent columns to numeric and ran basic regression

# Convert year columns to numeric
FinalMerge[,2001:2012] <- as.numeric(FinalMerge[,2001:2012])

# Need to figure out how to get rid of "-" in data

summary(FinalMerge)
# Run a regression
R1 <- lm(PercentNascent ~ PercentPerceived + PercentIntention, data = FinalMerge)
R1

>>>>

# Convert percent columns from character to numeric
FinalMerge[,"PercentPerceived"] <- as.numeric(FinalMerge[,"PercentPerceived"])
FinalMerge[,"PercentFear"] <- as.numeric(FinalMerge[,"PercentFear"])
FinalMerge[,"PercentNascent"] <- as.numeric(FinalMerge[,"PercentNascent"])
FinalMerge[,"PercentOwner"] <- as.numeric(FinalMerge[,"PercentOwner"])
FinalMerge[,"PercentIntention"] <- as.numeric(FinalMerge[,"PercentIntention"])

# Check data to confirm change
summary(FinalMerge)

# Run a linear regression
R1 <- lm(PercentNascent ~ PercentPerceived + PercentIntention, data = FinalMerge)
summary(R1)

# Calculate confidence intervals
confint(R1)
